Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-16 write-ups/PLDI/paper.tex
Tweaks.

\myfiglong\ref{fig:fine-grained-timing} reports, on three
configurations, the average gather and execution times for the non-cooperative
kernel w.r.t. the quantity of workgroups allocated to it.
A logarithmic
scale is used for time since gather times tend to be much smaller than
execution times. The horizontal grey lines indicates the desired period
for non-cooperative kernels.  These graphs show a representative sample of our results; the full set of graphs for all configurations is provided in Appendix~\ref{appendix:extraresponsiveness} (supplementary material).

@@

\paragraph{Performance} 
\myfiglong\ref{fig:performance} reports, for the Iris GPU, the overhead brought by the scheduling of
non-cooperative kernels over the cooperative kernel execution time.  This is the slowdown associated with running the cooperative kernel in the presence of multitasking, vs.\ running the cooperative kenrel in isolation (geometric mean over all applications and inputs).  We also show the period at which non-cooperative kernels can be scheduled (aritmetic mean over all applications
and inputs).
The results for the other GPUs are similar and are graphed in Appendix~\ref{appendix:extraperformance} (supplementary material).
 We show
results for the three workloads listed in
\mysec~\ref{sec:sizingnoncoop}. The two gray horizontal lines in the
period graph correspond to the period goals of the workloads: the higher
(resp. lower) line corresponds to a period of 70ms (resp. 40ms) for the
light (resp. medium and heavy) workload.

@@

\section{Graphs for Multitasking Experiments}

In \mysec\ref{sec:responsiveness} we showed a selection of graphs to illustrate our
experimental results related to performance and responsiveness.  Here
we present the full set of graphs.

\subsection{Responsiveness graphs}\label{appendix:extraresponsiveness}

@@

\ADComment{Tyler: show all the graphs, perhaps grouped by GPU.}

\subsection{Performance graphs}\label{appendix:extraperformance}

\myfiglong\ref{fig:performance} presents data on the performance impact and period associated with multitasking cooperative and non-cooperative workloads, for the Iris GPU.

\ADComment{Tyler: say something like ``Corresponding graphs for the XXX and YYY GPUs are shown in \myfigs\ref{ } and~\ref{ }, respectively.'', adding the graphs.}

>>>>

\myfiglong\ref{fig:fine-grained-timing} reports, on three
configurations, the average gather and execution times for the non-cooperative
kernel w.r.t. the quantity of workgroups allocated to it.
A logarithmic
scale is used for time since gather times tend to be much smaller than
execution times. The horizontal grey lines indicates the desired period
for non-cooperative kernels.  These graphs show a representative sample of our results; the full set of graphs for all configurations is provided in Appendix~\ref{appendix:extragraphs} (supplementary material).

@@

\paragraph{Performance} 
\myfiglong\ref{fig:performance} reports, for the Iris GPU, the overhead brought by the scheduling of
non-cooperative kernels over the cooperative kernel execution time.  This is the slowdown associated with running the cooperative kernel in the presence of multitasking, vs.\ running the cooperative kenrel in isolation (geometric mean over all applications and inputs).  We also show the period at which non-cooperative kernels can be scheduled (aritmetic mean over all applications
and inputs).
The results for the other GPUs are similar.
 We show
results for the three workloads listed in
\mysec~\ref{sec:sizingnoncoop}. The two gray horizontal lines in the
period graph correspond to the period goals of the workloads: the higher
(resp. lower) line corresponds to a period of 70ms (resp. 40ms) for the
light (resp. medium and heavy) workload.

@@

\section{Graphs for Multitasking Experiments}\label{appendix:extragraphhs}

@@

\ADComment{Tyler: show all the graphs.}
